### 2023-02-13 article.tex
Fix spelling

Hosted code commonly keeps a history of file changes,
This means that when a change is made to the code,
a new version is created. In the case that the change was harmful,
one can go back to an earlier version and continue again from there.
The version control system keeps track of who-did-what transparantly.
\iffalse
Figure \ref{fig:daisie_contributors}
shows the number of commits the authors of DAISIE (\cite{etienne2020daisie})
have made to its code.
\fi
It is a general recommendation to put version control
on all human-produced data (\cite{wilson2014best}),
as well as openly working on the code from the start (\cite{jimenez2017four}).
Half of the published code has such a version control 
system (\cite{stodden2018empirical}).

@@

One problem that containers have, is their size:
they can be several gigabytes big. 
This makes the distribution of these containers harder.
Ideally, containers are stored online and distributed in
standardised ways.
Although progress is being made, 
there is no way to do so for all container types.
Additionally, probably due to their novely,
container hosting sites lack metadata.

>>>>

Hosted code commonly keeps a history of file changes,
This means that when a change is made to the code,
a new version is created. In the case that the change was harmful,
one can go back to an earlier version and continue again from there.
The version control system keeps track of who-did-what transparently.
\iffalse
Figure \ref{fig:daisie_contributors}
shows the number of commits the authors of DAISIE (\cite{etienne2020daisie})
have made to its code.
\fi
It is a general recommendation to put version control
on all human-produced data (\cite{wilson2014best}),
as well as openly working on the code from the start (\cite{jimenez2017four}).
Half of the published code has such a version control 
system (\cite{stodden2018empirical}).

@@

One problem that containers have, is their size:
they can be several gigabytes big. 
This makes the distribution of these containers harder.
Ideally, containers are stored online and distributed in
standardised ways.
Although progress is being made, 
there is no way to do so for all container types.
Additionally, probably due to their novelty,
container hosting sites lack metadata.
